Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-09 R0V0.tex
Remove the paragraph explaining the notation of the set Xi for the fully decentralized case. Start to explain the decomposition of the MI (8) into cliques.
Finish explaining clique decomposition. Start to change decentralized case in example.

In case of full decentralization with $n_i=m_i=1$, for every index $i\in\mathbb{N}_{[1,N]}$,  the set $\Xi$ is defined with $\mathbf{C}_j=\{e_j\}$, $\mathscr{K}(i)=\{i\}$ and $\mathbf{X}(\mathscr{K}(i))=\{x_i\}$.

@@

For the remaining cases, the structure of the network composed of systems of the form \eqref{eq:example}. More specifically, Proposition~\ref{prop:clique tree decomposition} can be employed, as the graph describing the interconnection of the network is a subclass of chordal graphs.

The constraints imposed on the matrix $Y$ are such that the matrix of the left-hand-side of the MI \eqref{eq:MI formulation} is given by
\begin{equation*}
	\mathbin{\mathtt{diag}}\left(\begin{bmatrix}
		T_{11}&T_{12}\\
		T_{12}^\top&T_{22}
	\end{bmatrix},\cdots,\begin{bmatrix}
		T_{(N-1)(N-1)}&T_{(N-1)N}\\
		T_{(N-1)N}^\top&T_{NN}
	\end{bmatrix}\right).
\end{equation*}

@@

In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI \eqref{eq:MI formulation} was 2.6 seconds. In this case, $\mathscr{K}_Y(i)=\{j\in\mathbb{N}_{[1,N]}\setminus\mathscr{K}(i):Y_{ij}\equiv0\}$, where $\mathscr{K}(i)=\{i\}$. Solving the MI \eqref{eq:MI formulation} the following components the matrices $W$ and $Y$ were obtained
\begin{align*}
 W=&\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),\\
 Y=&\mathbin{\mathtt{diag}}\left(Y_1,Y_2,Y_3,Y_4\right)
\end{align*}
where
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.4,1.6\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
\end{equation*}
and, for each index $i=1,4$,
\begin{align*}
 Y_i(q_i)=[-3.1y_i+0.06x_iy_i,-3.6-0.02x_i-2.3y_i^2-2.4x_i^2]
\end{align*}
and, for each index $i=2,3$,
\begin{align*}
 Y_i(q_i)=[-3.1y_i,-3.8-2.1y_i^2-2.2x_i^2].
\end{align*}

>>>>

@@

For the remaining cases, the structure of the network composed of systems of the form \eqref{eq:example}. More specifically, Proposition~\ref{prop:clique tree decomposition} can be employed, as the graph describing the interconnection of the network is a subclass of chordal graphs. Consequently, the MI~\eqref{eq:MI formulation} can be decomposed into $N-1$ cliques  described by the matrix
\begin{equation*}
	F_k=\begin{bmatrix}
		F_{11}&F_{12}\\
		F_{12}^\top&F_{22}
	\end{bmatrix}\;.
\end{equation*}

@@

In the last case, the fully decentralized scenario has been considered. The time taken by the parser to solve the MI~\eqref{eq:MI formulation} was 2.6 seconds. In this case, $\mathscr{K}(i)=\{i\}$, 
\begin{equation*}
	\begin{array}{rl}
		\mathbf{C}_1=\mathbf{C}_2=\{e_1\},&\mathbf{C}_3=\mathbf{C}_4=\{e_2\},\\
		\mathbf{C}_5=\mathbf{C}_6=\{e_3\},&\mathbf{C}_7=\mathbf{C}_8=\{e_4\}
	\end{array}
\end{equation*}
Solving the MI \eqref{eq:MI formulation} the following components the matrices $W$ and $Y$ were obtained
\begin{align*}
 W=&\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),\\
 Y=&\mathbin{\mathtt{diag}}\left(Y_1,Y_2,Y_3,Y_4\right)
\end{align*}
where
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.4,1.6\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.2,1.6\right)
\end{equation*}
and, for each index $i=1,4$,
\begin{align*}
 Y_i(q_i)=[-3.1y_i+0.06x_iy_i,-3.6-0.02x_i-2.3y_i^2-2.4x_i^2]
\end{align*}
and, for each index $i=2,3$,
\begin{align*}
 Y_i(q_i)=[-3.1y_i,-3.8-2.1y_i^2-2.2x_i^2].
\end{align*}
